Blocking-resistant communication\\through domain fronting

### 2014-08-02 docs/meek.tex
Prevent line breaks in "X-Session-Id".

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver must handle many clients at once,
and therefore maintains many open connections to a local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not of the actual client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit session ID for each new Tor stream,
which it sends with its requests in a special
X-Session-Id HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.

>>>>

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

\meekserver must handle many clients at once,
and therefore maintains many open connections to a local Tor process,
one for each active client.
When a new request arrives, the server must determine which
open session it belongs to
(or whether it is a brand-new client needing a new session).
In TCP, different streams are distinguished by their
(source~IP, source port, dest~IP, dest~port) tuple,
but that doesn't work for \meek, for two reasons:
the source IP of the requests is that of the intermediate web service,
not of the actual client;
and a logical stream is chopped into multiple independent HTTP requests,
so the source port is always changing.
Instead, each client generates a random 256-bit session ID for each new Tor stream,
which it sends with its requests in a special
\mbox{X-Session-Id} HTTP header.
\meekserver, when it sees a session ID for the first time,
opens up a new connection to the local Tor process
and associates the connection and ID in a cache.
Subsequent requests with the
same session ID will reuse the same Tor connection.
Sessions are closed after a period of inactivity.
Figure~\ref{fig:protocol} shows a sample of the protocol.
